### 2024-06-15 conteudo/background/codeduplication.tex
format a little bit the weird things done before

\begin{itemize}
	\item \textbf{Type-1:} The differences between F and G are in the context of revision of comments, variable names, white spaces and any other kind of irrelevant elements. (ADD FIGURE) shows a typical example of Type-1 Code Duplication \citep{litreview}.

	\item \textbf{Type-2:} The differences between F and G is the same as the type-1, with the addition of considering addition and deletion of redudant codes. (ADD FIGURE) shows a typical example of Type-2 Code Duplication \citep{litreview}.

	\item \textbf{Type-3:} The difference between F and G is the same as the type-2, with the addition of considering the reorder of code blocks as well as statements within code blocks. (ADD FIGURE) shows a typical example of Type-3 Code Duplication \citep{litreview}.

	\item \textbf{Type-4:} The difference between F and G is the same as the type-3, with the addtionf of considering changes on data sctrucure, the order of operands/operators in expresssions, or replacing part of codes with equivalent composition. (ADD FIGURE) shows a typical example of Type-4 Code Duplication \citep{litreview}. 
\end{itemize}

>>>>

\begin{itemize}
	\begin{item}
		\textbf{Type-1:} The differences between F and G are in the context of revision of comments, variable names, white spaces 
		and any other kind of irrelevant elements. (ADD FIGURE) shows a typical example of Type-1 Code 
		Duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-2:} The differences between F and G is the same as the type-1, with the addition of considering 
		addition and deletion of redudant codes. (ADD FIGURE) shows a typical example of Type-2 Code Duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-3:} The difference between F and G is the same as the type-2, with the addition of considering 
		the reorder of code blocks as well as statements within code blocks. (ADD FIGURE) shows a typical example of 
		Type-3 Code Duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-4:} The difference between F and G is the same as the type-3, with the addition of considering 
		changes on data sctrucure, the order of operands/operators in expresssions, or replacing part of codes with 
		equivalent composition. (ADD FIGURE) shows a typical example of Type-4 Code Duplication \citep{litreview}. 
	\end{item}

\end{itemize}
